Evaluation of dynamic resource allocation strategies for overlay Apache Spark clusters on HPC

### 2019-05-03 paper.tex
some methods text

\section{Materials and Methods}\label{sec:methods}
    SPA consists of a Python-based driver with bash-templates that are called 
    using the Slurmpy~\cite{slurmpy} library. In order to commence pilot-scheduling,
    the user must supply the bash template of choice and a JSON configuration 
    file which contains details on pilot node requirements and the desired application
    to be launched. Currently, there only exists a single pilot template for launching
    Spark jobs on a Slurm-based HPC cluster. The pseudocode for that template can 
    be seen in ~\ref{Figure:pilot-temp}.
    \todo{walltime parameter of workflow}
    \subsection{Added value of pilot scheduling}
        \todo{execution of a batch cluster vs dynamic (pilot) cluster}
    \subsection{Robust masters}
        \todo{scala standalone vs our pyspark workaround. kill masters in experiments}
    \subsection{Checkpointing}
        \todo{metric for determining how often to checkpoint based on cluster size}
    \subsection{Job arrays}
        \todo{need to kill idle workers. may not want all workers to be running at once.}
    \subsection{Example application}
        \todo{incrementation with varying task durations}
\section{Discussion}\label{sec:discussion}
\section{Conclusion}\label{sec:conclusion}

>>>>

\section{Materials and Methods}\label{sec:methods}

    In order to compare and contrast pilot over batch scheduling for scientific 
    computing, we first created a synthetic application that would process the 
    Big Brain~\cite{bigBrain}, a 76G 3D histological image of a human brain. The algorithm
    is described in~\ref{Figure:incrementation}. This algorithm was selected as 
    it would give us the flexibility to easily vary computing time as needed.

    For the batch submission script, we reused the once recommended on the
    compute canada wiki ~\cite{wiki}.

    \todo{walltime parameter of workflow}
    \subsection{Added value of pilot scheduling}
        \todo{execution of a batch cluster vs dynamic (pilot) cluster}
    \subsection{Robust masters}
        \todo{scala standalone vs our pyspark workaround. kill masters in experiments}
    \subsection{Checkpointing}
        \todo{metric for determining how often to checkpoint based on cluster size}
    \subsection{Job arrays}
        \todo{need to kill idle workers. may not want all workers to be running at once.}
    \subsection{Example application}
        \todo{incrementation with varying task durations}
\section{Discussion}\label{sec:discussion}
\section{Conclusion}\label{sec:conclusion}
